The evolution of the transcriptome of mammalian placentas

### 2016-10-04 manuscript/manuscript.Rnw
update manuscript for gsea
explain GSEA and ANOVA for morphology

>>>>

Significant shifts in expression levels which correlate with placenta
morphology (shape, interdigitation, and intimacy) were identified
using ANOVA on generalized linear models with the $\log$ \ac{FPKM} as
the response variable and the morphology as the predictor variable.
Placenta morphology with a defined order (interdigitation, intimacy)
were additionally analyzed using proportional odds logistic regression
using the MASS package in R~\cite{Venables2002:MASS}.

\subsection{Gene Set and Pathway Enrichment Analysis}

Gene sets and pathways in were obtained from MSigdb v5.1 hallmark gene
set \cite{Liberzon.ea2011:MolecularsignaturesdatabaseMSigDB} and Gene
Ontology which represent a superset of available pathway databases,
including Reactome, Kegg, Netpath, and GO. We calculated the
over-representation of gene lists in these gene sets using Fisher's
exact test and corrected for multiple testing by estimating the
\ac{FDR} using the Benjamini and Hochberg procedure
\cite{Benjamini1995:bh_procedure}.
